MSAD_PCA_Walkthrough

### 2017-07-04 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Created a LaTeX vignette folder. In the LaTeX vignette, I am building the package 'mvMonitoring' with devtools::build(), so if the LaTeX vignette is in the proper vignettes folder, it will recursively attempt to build itself. This is bad.

\documentclass{report}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}
\usepackage{enumerate}

\begin{document}

@@

This section provides a fully commented code walk-through for the main \texttt{msp*} functions in the \texttt{mvMonitoring} package. This package depends on a few other packages, but most of these dependencies are on commonly-used packages. The exception is \texttt{BMS}.
<<r load_mvMonitoring>>=
library(devtools)
# install.packages("BMS") # If necessary
build("C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring")
library(mvMonitoring)
@

@@

<<r generate_Data>>=
fault1A_xts <- mspProcessData(faults = "A1",
                              period = 7 * 24 * 60,
                              faultStartIndex = 8500,
                              startTime = "2015-05-16 10:00:00 CST")
str(fault1A_xts)
@

@@

Furthermore, the \texttt{Dynamic = TRUE} option means that the \texttt{mspTrain} function will include the lags specified by the \texttt{lagsIncluded} argument. Finally, the number of sequential anomalous observations necessary to raise an alarm is set at 5 by the \texttt{faultsToTriggerAlarm} argument. These last three arguments are set to their defaults.
<<r train>>=
train1A_xts <- fault1A_xts[1:8461,]
# This function will run in 13 seconds on the author's machine.
train1A_ls <- mspTrain(data = train1A_xts[,-1],
                       labelVector = train1A_xts[,1],
                       trainObs = 3 * 24 * 60,
                       updateFreq = 1 * 24 * 60,
                       Dynamic = TRUE,
                       lagsIncluded = 0:1,
                       faultsToTriggerAlarm = 5)
@
The \texttt{mspTrain} function returns a list of four objects:
\begin{enumerate}
\item \texttt{FaultChecks}: An \texttt{xts} matrix of monitoring statistics and associated indicators for all observations after the burn-in of \texttt{trainObs}. It will have 10080 - \texttt{trainObs} number of rows and five columns:
	\begin{enumerate}
	\item \texttt{SPE}: the SPE statistic for each observation.
    %
    \item \texttt{SPE\_Flag}: an indicator showing if the SPE statistic for that observation is beyond the calculated threshold; 0 is normal, 1 is flagged.
    %
    \item \texttt{T2}: the $T^2$ statistic for each observation.
    %
    \item \texttt{T2\_Flag}: an indicator showing if the $T^2$ statistic for that observation is beyond the calculated threshold; 0 is normal, 1 is flagged.
    %
    \item \texttt{Alarm}: an indicator showing if the observation is in a sequence of flagged observations; 0 is normal, 1 is alarmed.
	\end{enumerate}
%
\item \texttt{Non\_Alarmed\_Obs}: An \texttt{xts} matrix will all observations with an alarm code of 0 from \texttt{FaultChecks}. Of note, this matrix contains the data, while the \texttt{FaultChecks} matrix only contains the monitoring statistics and indicators.
%
\item \texttt{Alarms}: An \texttt{xts} matrix of all the observations removed from the training data matrix.
%
\item \texttt{TrainingSpecs}: a list with length equal to the number of classes -- in this case 3. For each class, this list contains a list of six objects:
	\begin{enumerate}
	\item \texttt{SPE\_Threshold}: a named numeric scalar of the $1 - \alpha$ percentile of the non-parametric estimate of the SPE statistic density.
    %
    \item \texttt{T2\_Threshold}: a named numeric scalar of the $1 - \alpha$ percentile of the non-parametric estimate of the $T^2$ statistic density.
    %
    \item \texttt{projectionMatrix}: The $p \times q$ matrix of eigenvectors necessary to project a $p$-dimensional observation to $q$ dimensions. This is necessary to reduce the dimension of any test observation, and is used in calculating the SPE statistic for test observations.
    %
    \item \texttt{LambdaInv}: The inverse of the diagonal $q \times q$ matrix of eigenvalues. This matrix is used to calculate the $T^2$ statistic for test observations.
    %
    \item \texttt{muTrain}: The mean vector of the training observations. This is used to center the test observations on the training mean.
    %
    \item \texttt{RootPrecisTrain}: The $p \times p$ diagonal matrix of the inverse square roots of the feature variances. This is used to scale the test observations into the training scale.
	\end{enumerate}
\end{enumerate}

>>>>

\documentclass{report}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}
\usepackage{enumerate}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

This section provides a fully commented code walk-through for the main \texttt{msp*} functions in the \texttt{mvMonitoring} package. This package depends on a few other packages, but most of these dependencies are on commonly-used packages. The exception is \texttt{BMS}.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(devtools)}
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'devtools' was built under R version 3.4.1}}\begin{alltt}
\hlcom{# install.packages("BMS") # If necessary}
\hlkwd{build}\hlstd{(}\hlstr{"C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring"}\hlstd{)}
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# "{}C:/PROGRA\textasciitilde{}1/R/R-34\textasciitilde{}1.0/bin/x64/R"{} --no-site-file --no-environ --no-save\ \ \textbackslash{}\\\#\#\ \  --no-restore --quiet CMD build\ \ \textbackslash{}\\\#\#\ \  "{}C:\textbackslash{}Users\textbackslash{}gabriel\_odom\textbackslash{}Documents\textbackslash{}GitHub\textbackslash{}mvMonitoring\textbackslash{}mvMonitoring"{}\ \ \textbackslash{}\\\#\#\ \  --no-resave-data --no-manual}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# }}\begin{verbatim}
## [1] "C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring_0.1.0.tar.gz"
\end{verbatim}
\begin{alltt}
\hlkwd{library}\hlstd{(mvMonitoring)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fault1A_xts} \hlkwb{<-} \hlkwd{mspProcessData}\hlstd{(}\hlkwc{faults} \hlstd{=} \hlstr{"A1"}\hlstd{,}
                              \hlkwc{period} \hlstd{=} \hlnum{7} \hlopt{*} \hlnum{24} \hlopt{*} \hlnum{60}\hlstd{,}
                              \hlkwc{faultStartIndex} \hlstd{=} \hlnum{8500}\hlstd{,}
                              \hlkwc{startTime} \hlstd{=} \hlstr{"2015-05-16 10:00:00 CST"}\hlstd{)}
\hlkwd{str}\hlstd{(fault1A_xts)}
\end{alltt}
\begin{verbatim}
## An 'xts' object on 2015-05-16 10:00:00/2015-05-23 09:59:00 containing:
##   Data: num [1:10080, 1:4] 1 1 1 1 1 1 1 1 1 1 ...
##  - attr(*, "dimnames")=List of 2
##   ..$ : NULL
##   ..$ : chr [1:4] "state" "x" "y" "z"
##   Indexed by objects of class: [POSIXct,POSIXt] TZ: 
##   xts Attributes:  
##  NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

Furthermore, the \texttt{Dynamic = TRUE} option means that the \texttt{mspTrain} function will include the lags specified by the \texttt{lagsIncluded} argument. Finally, the number of sequential anomalous observations necessary to raise an alarm is set at 5 by the \texttt{faultsToTriggerAlarm} argument. These last three arguments are set to their defaults.
% ```{r}
% train1A_xts <- fault1A_xts[1:8461,]
% # This function will run in 13 seconds on the author's machine.
% train1A_ls <- mspTrain(data = train1A_xts[,-1],
%                        labelVector = train1A_xts[,1],
%                        trainObs = 3 * 24 * 60,
%                        updateFreq = 1 * 24 * 60,
%                        Dynamic = TRUE,
%                        lagsIncluded = 0:1,
%                        faultsToTriggerAlarm = 5)
% ```
The \texttt{mspTrain} function returns a list of four objects:
\begin{enumerate}
\item \texttt{FaultChecks}: An \texttt{xts} matrix of monitoring statistics and associated indicators for all observations after the burn-in of \texttt{trainObs}. It will have 10080 - \texttt{trainObs} number of rows and five columns:
	\begin{enumerate}
	\item \texttt{SPE}: the SPE statistic for each observation.
    %
    \item \texttt{SPE\_Flag}: an indicator showing if the SPE statistic for that observation is beyond the calculated threshold; 0 is normal, 1 is flagged.
    %
    \item \texttt{T2}: the $T^2$ statistic for each observation.
    %
    \item \texttt{T2\_Flag}: an indicator showing if the $T^2$ statistic for that observation is beyond the calculated threshold; 0 is normal, 1 is flagged.
    %
    \item \texttt{Alarm}: an indicator showing if the observation is in a sequence of flagged observations; 0 is normal, 1 is alarmed.
	\end{enumerate}
%
\item \texttt{Non\_Alarmed\_Obs}: An \texttt{xts} matrix will all observations with an alarm code of 0 from \texttt{FaultChecks}. Of note, this matrix contains the data, while the \texttt{FaultChecks} matrix only contains the monitoring statistics and indicators.
%
\item \texttt{Alarms}: An \texttt{xts} matrix of all the observations removed from the training data matrix.
%
\item \texttt{TrainingSpecs}: a list with length equal to the number of classes -- in this case 3. For each class, this list contains a list of six objects:
	\begin{enumerate}
	\item \texttt{SPE\_Threshold}: a named numeric scalar of the $1 - \alpha$ percentile of the non-parametric estimate of the SPE statistic density.
    %
    \item \texttt{T2\_Threshold}: a named numeric scalar of the $1 - \alpha$ percentile of the non-parametric estimate of the $T^2$ statistic density.
    %
    \item \texttt{projectionMatrix}: The $p \times q$ matrix of eigenvectors necessary to project a $p$-dimensional observation to $q$ dimensions. This is necessary to reduce the dimension of any test observation, and is used in calculating the SPE statistic for test observations.
    %
    \item \texttt{LambdaInv}: The inverse of the diagonal $q \times q$ matrix of eigenvalues. This matrix is used to calculate the $T^2$ statistic for test observations.
    %
    \item \texttt{muTrain}: The mean vector of the training observations. This is used to center the test observations on the training mean.
    %
    \item \texttt{RootPrecisTrain}: The $p \times p$ diagonal matrix of the inverse square roots of the feature variances. This is used to scale the test observations into the training scale.
	\end{enumerate}
\end{enumerate}
